\documentclass{res} 

\usepackage{utopia}
% used to create the lines
\usepackage{graphics}

% used to create links
\usepackage{hyperref} 

% used to make section titles small caps
\renewcommand{\sectionfont}{\bfseries\scshape}

% set the space between sections
\renewcommand{\sectionskip}{0.2 in}

% set the width of text portion
\setlength{\textwidth}{5.1in} 

\begin{document}
\begin{resume}
\centerline{\bfseries\Large Roommate Agreement}

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
\begin{enumerate}
\item Thou shalth noth kill thy ro\"{o}mmaet (withouth c{\o}nsent). Even if he snoreth or thou shalth fetch straighth A's as a consequence.
\item You do not masturbate in the room and should rarely get boners save the morning glory.
\item If no one is in the room at least one window shall remain open to let off the bad smell of the three of us' testicle smells combined. However, if it is raining or snowing this rule is disregarded.
\item You are not allowed to go through your roommate's laptop. Except for April Fools' Day.
\item You restrict your farts in the room and minimize the diffusing of stink from your potentially smelly clothing.
\item You need permission from respective roommates to play music and this permission may be revoked.
\item Tuesdays are tickle-your-roommate days.
\item Studying at night while roommates are sleeping involves only using desk light, if permitted.
\item No smoking in the room, drinking only with permission.
\item No shows of affection (No gay shit).
\item No stealing from roommates :-)
\item Eating roommates' food conducted only by consent, unless the cost was shared.
\item Saturdays are teach-Yusuf-Turkish days.
\item No taking pictures of roommates in the room without consent.
\item DOTA2 players are lame.
\item The password to WIFI in the room is 12893256.
\item On the nights of full moon, the roommates shall hold council and make amendments to the agreement.
\item No insults in the room unless it is funny or the situation is such that it is necessary or it is directed at the infamous ruling party, BJP (Blowjob Party? [citation needed])of India.
\item Roommates should put in an effort to be as quiet as possible in the room when one of the roommates is sleeping/studying.
\item The residents of Room 117 at Dormitory 77 reserve the right to amend the existing rules and add new rules if necessary. The roommates shall retain push access to the repository at http://github.com/cagdasoztekin/roommate-agreement as long as they remain residence at the room of interest and remain faithful to the Roommate Agreement.

\end{enumerate}


% bottom part
 \vfill
 
% the bottom line
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}

% footnote
\centerline{ 
	Room 117, Dorm 77, Bilkent University. Latest version could be found at http://cgds.me/roommate-agreement.pdf
}


\end{resume}

\end{document}
